\chapter*{General Conclusion}
\addcontentsline{toc}{chapter}{General Conclusion}
\markboth{General Conclusion}{}
The project successfully transitioned the deployment process from a manual system to a streamlined, automated approach. This was achieved by adopting a DevOps methodology, leveraging cloud infrastructure, and implementing modern tools. The initial groundwork has been laid by provisioning the cloud environment and establishing a CI/CD pipeline.  Future efforts will focus on building and deploying the web application within this new framework.
\par
Personally and professionally, this project provided me valuable learning experiences. It highlighted the importance of collaboration between development and operations teams (DevOps)  for efficient software delivery.  I gained practical experience with cloud computing tools like Terraform and GitLab, along with continuous integration and delivery (CI/CD) practices.
\par
The world of DevOps is constantly evolving, and there's always room to push the boundaries.  One intriguing idea would be to develop a developer-centric interface that integrates directly with the CI/CD pipeline. This interface could provide real-time feedback on code quality, suggest deployment strategies based on historical data, and even automate some aspects of the deployment process itself.  Imagine a scenario where developers could visually drag and drop code modules to create deployment pipelines, or receive automated recommendations for infrastructure configurations based on their application's resource requirements. By building an intelligent and interactive interface, we could empower developers to take ownership of the deployment process while still maintaining governance and security best practices.
