
%=== File containing Global Configuration of the report ===%
%                                                          %
% Copyright (C) ISI - All Rights Reserved                  %
% Proprietary                                              %
% Written by Med Hossam <med.hossam@gmail.com>, April 2016 %
%                                                          %
% @author: HEDHILI Med Houssemeddine                       %
% @linkedin: http://tn.linkedin.com/in/medhossam           %
%==========================================================%

%=========== You MUST type your information here ==========%
% global_config.tex file is designed to configure your     %
% cover pages (main, back and black covers)                %
%==========================================================%

%============= Config new columns type ==============%
\newcolumntype{L}{>{\raggedright\arraybackslash}}
\newcolumntype{R}{>{\raggedleft\arraybackslash}}
\newcolumntype{C}{>{\centering\arraybackslash}}
\renewcommand{\labelitemi}{\ding{227}}
%==================================================%

%========= Config the cover section ==========%

\title{Orchestrating Critical Application Deployment with Minimal Downtime}

\author{Ben Hadj Nasr Mohamed}
%%% if necessary
% Set isBinomal to true and type second author name
%\setboolean{isBinomal}{true}
%\secondAuthor{Prénom NOM}

\diplomaName{Diplôme National d'Ingénieur en Sciences Appliquées et Technologiques}
\speciality{Computer Science and Engineering}

%% Encadrant professionnel
\proFramerName{Yazid Missaoui}
\proFramerSpeciality{Ingénieur R\&D}

%% Encadrant académique
\academicFramerName{Monsieur/Madame Prénom NOM}
\academicFramerSpeciality{Maître Assistant(e)}

%% Entreprise d'accueil
\companyName{Adactim}

%% Année universitaire
\collegeYear{2023 - 2024}

%%%%%% Signatures section %%%%%%

% You can simply remove theses sentences by typing an empty string
% \proSignSentence{}

\proSignSentence{I authorize the student to submit his internship report.}

\academicSignSentence{I authorize the student to submit his internship report.}

%%% EN
\englishAbstract{Put the English abstract here, put the English abstract here, put the English abstract here, put the English abstract here, put the English abstract here, put the English abstract here... Please don't exceed ten lines, Please don't exceed ten lines, Please don't exceed ten lines, Please don't exceed ten lines. Put the English abstract here, please don't exceed ten lines. Put the English abstract here, please don't exceed ten lines. Put the English abstract here, please don't exceed ten lines. Put the English abstract here, please don't exceed ten lines. Put the English abstract here, please don't exceed ten lines. Put the English abstract here, please don't exceed ten lines. Put the English abstract here, please don't exceed ten lines. Put the English abstract here, please don't exceed ten lines.}

\englishAbstractKeywords{Please don't use more than five keywords}

%% if you want to get rid of the company address just set the boolean variable to false
% PS : it's optional
\setboolean{wantToTypeCompanyAddress}{true}

\companyEmail{https://adactim.com/home/}
\companyTel{+216 31 34 00 00}
\companyFax{+216 70 72 11 63}
\companyAddressFR{Technopark El Ghazela Tunis - Tunisia Tunis، 2088}